%-------------------------
% Resume in LateX
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % Clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate PDF is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

% Just in case someone needs a heading that does not need to be in a list
\newcommand{\resumeHeading}[4]{
    \begin{tabular*}{0.99\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large TRAN CONG HOAN}} & Email: \href{mailto:tranconghoan0607@gmail.com}{tranconghoan0607@gmail.com}\\
  \href{https://www.linkedin.com/in/hoan-tran-cong-328b79b8}{linkedin.com/hoan-tran-cong} & Mobile: \href{tel:+84369351696}{+84-369-351-696} \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Post and Telecommunication Institute of Technology}{Ho Chi Minh City, Viet Nam}
      {Software Technology; GPA: 3.6}{Oct 2013 - Dec 2016}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Hansen Technologies}{Thao Dien, Thu Duc City, Ho Chi Minh City, Viet Nam}
      {Senior Software Engineer}{August 2023 - Present}
      \resumeItemListStart
        \resumeItem{CCB-I}
          {Hansen CCB for Pay Media provides customer care and billing for pay media services, supporting multiple business models and enabling seamless integration with OTT partners. Led the design and development of new features and maintained existing functionality. Collaborated with architects on solution design, conducted systems analysis, and followed the full SDLC. Created technical documentation using flowcharts and diagrams. Mentored junior and mid-level engineers, and worked cross-functionally within Agile/Scrum teams to ensure timely delivery.}
      \resumeItemListEnd

% --------Multiple Positions Heading------------
    % \resumeSubSubheading
    %   {Software Engineer}{August 2023 - Sep 2024}
    %   \resumeItemListStart
    %     \resumeItem{CCB-}
    %       {CCB-I is xxx.}
    %   \resumeItemListEnd

%-------------------------------------------

    \resumeSubheading
      {MTI Technology}{Tan Binh, Ho Chi Minh City, Viet Nam}
      {Software Engineer}{March 2019 - July 2023}
      \resumeItemListStart
        \resumeItem{music.jp}
          {music.jp is an entertainment web application that provides users with access to a wide range of music, video, comic and book content. Collaborated with SCRUM teams on requirement discussions, planning, and retrospectives. Designed class diagrams, developed full-stack features, performed code reviews, and conducted unit testing. Worked closely with technical leads and clients to resolve complex issues.
          Gained proficiency in C\# and ASP.NET MVC, utilized AWS and Azure for cloud solutions, applied design patterns and SOLID principles, and enhanced performance through Docker deployments and Redis caching.}
        \resumeItem{Jiimo - Vaccination Web Application}
          {Jiimo is a web application that helps users to manage their vaccination schedule. It provides features such as reminders, tracking, and reporting.}
      \resumeItemListEnd

    \resumeSubheading
      {TTP Solutions}{Dist 12, Ho Chi Minh City, Viet Nam}
      {Software Engineer}{Oct 2016 - Mar 2019}
      \resumeItemListStart
        \resumeItem{Warehouse Management System}
          {An application that helps users to manage their warehouse operations. It provides features such as inventory management, order processing, and reporting. Worked closely with BAs and SCRUM teams to analyze requirements, designed class diagrams for system architecture, developed and unit-tested features, implemented RESTful APIs with detailed documentation, and performed code reviews and refactoring for maintainability and performance.}
      \resumeItemListEnd

    \resumeSubheading
      {GLOBAL CYBERSOFT}{Dist 12, Ho Chi Minh City, Viet Nam}
      {Software Engineer}{Aug 2016 - Aug 2018}
      \resumeItemListStart
        \resumeItem{NADAE - .NET ADAPTIVE DISTRIBUTE APPLICATION ENVIRONMENT}
          {A large-scale project focused on creating a framework to support the deployment of distributed systems. This involved the integration of multiple components and seamless collaboration across cross-functional teams to meet dynamic requirements.
          Designed class diagrams to support feature development, collaborated cross-functionally to resolve complex technical issues, assisted both development and QC teams during testing, and maintained project momentum under tight deadlines and changing requirements.}
        \resumeItem{HRM System}
          {A web-based Human Resource Management System (HRMS) that allows users to manage employee information, attendance, payroll, and performance evaluations. The system is designed to streamline HR processes and improve efficiency.}
      \resumeItemListEnd

    \resumeSubheading
      {ECEPVN, LLC}{Dist 5, Ho Chi Minh City, Viet Nam}
      {Fresher Developer}{Mar 2016 - Jun 2016}
      \resumeItemListStart
        \resumeItem{Fresher Web Developer -- E-learning Platform}
          {Developed features of a web application for an e-learning platform using PHP and MySQL. The application allows users to create and manage courses, quizzes, and assignments. Learning about web development technology and language: HTML5, CSS, JS, Bootstrap, PHP, MySql, C\# and ASP.NET MVC.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Cargo Wise Midlleware}
      {Cargo Wise is a global leader in logistics and supply chain management software. The project involved the development of a middleware solution to integrate various systems and improve data flow between them.}
    \resumeSubItem{WorkFlow Management System}
      {A web-based application that allows users to create, manage, and track workflows. The system provides features such as task assignment, progress tracking, and reporting.}
  \resumeSubHeadingListEnd

% --------SKILLS------------
\section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: C\#, JavaScript, HTML5, CSS3, SQL.}
    }
    \item{
      \textbf{.NET Ecosystem}{: ASP.NET Core MVC, ASP.NET Core Web API, Core WCF, .NET Framework.}
    }
    \item{
      \textbf{Frontend Frameworks \& Libraries}{: Angular, ReactJS, VueJS, NuxtJS.}
    }
    \item{
      \textbf{Database Technologies}{: MSSQL, Oracle, PostgreSQL, MySQL.}
    }
    \item{
      \textbf{Containerization \& DevOps}{: Docker.}
    }
    \item{
      \textbf{Development Methodologies}{: Agile, Scrum.}
    }
    \item{
      \textbf{Cloud Platforms}{: AWS, Azure.}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
